### 2024-04-08 README.qmd
No warnings

```{r}
#| echo: false
#| eval: false
# Package setup:
usethis::use_description()
usethis::use_package("sf")
usethis::use_package("stplanr")
usethis::use_package("ggplot2")
usethis::use_package("dplyr")
usethis::use_r("opsnap")

@@

# Function to clean up column names

d_locations = d |>
  dplyr::pull(`OFF LOCATION`) |>
  head(10) |>
  lapply(FUN = stplanr::geo_code)
# d_geocoded = d |>
#   tidygeocoder::geocode("OFF LOCATION")
d_locations[[1]]
matrix(d_locations[[1]], ncol = 2)
sf::st_point(matrix(d_locations[[1]], ncol = 2))
d_locations_lengths = sapply(d_locations, function(x) {
    length(x)
    })

d_sf = lapply(d_locations[d_locations_lengths > 0], function(x) {
  sf::st_point(matrix(x, ncol = 2))
})
d_sfc = sf::st_sfc(d_sf) |>
    sf::st_sf(crs = "EPSG:4326")
d_sf = sf::st_sf(
    d |> slice(1:10) |> filter(d_locations_lengths > 0),
    geometry = d_sfc |> sf::st_geometry()
)

mapview::mapview(d_sf)
```

>>>>

```{r}
#| echo: false
#| eval: false
# Package setup:
usethis::use_description()
usethis::use_package("sf")
usethis::use_package("stplanr")
usethis::use_package("ggplot2")
usethis::use_package("dplyr")
usethis::use_r("opsnap")
# MIT license:
usethis::use_mit_license("Leeds Institute for Transport Studies")

@@

```{r}
# Function to clean up column names
d_sample = d[1:50, ]
d_sf = opsnap:::op_geocode(d_sample)
mapview::mapview(d_sf)
```
